Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-02-29 manuscript/appendix.Rmd
fixed up Table S1

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("tables_figures/climate_variables.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE, caption = "Table S1. Climate variable definitions, sources, and abbreviations", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12) %>%
  column_spec(1, width = "6cm") %>%
  column_spec(2, width = "2cm") %>%
  column_spec(3, width = "7cm") %>%
  column_spec(4, width = "2cm")
```
\elandscape
\newpage

>>>>

```{r eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
S1 <- read.csv("tables_figures/climate_variables.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(S1, format = "latex", booktabs = TRUE, caption = "Table S1. Climate variable definitions, sources, and abbreviations", escape = F)%>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  column_spec(1, width = "2.5cm") %>%
  column_spec(2, width = "5cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "7cm") %>%
  column_spec(5, width = "5cm")
```
\elandscape
\newpage
